\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2023-11-15 doc/USER_MANUAL/02_getting_started.tex
updates doc

If you have problems configuring the code on a Cray machine, i.e. for instance if you get an error message from the \texttt{configure} script, try exporting these two variables:
\texttt{MPI\_INC=\${CRAY\_MPICH2\_DIR}/include and FCLIBS=" "}, and for more details if needed you can refer to the \texttt{utils/Cray\_compiler\_information} directory.
You can also have a look at the configure script called:\newline
\texttt{utils/Cray\_compiler\_information/configure\_SPECFEM\_for\_Piz\_Daint.bash}.

>>>>

If you have problems configuring the code on a Cray machine, i.e. for instance if you get an error message from the \texttt{configure} script, try exporting these two variables:
\texttt{MPI\_INC=\${CRAY\_MPICH2\_DIR}/include and FCLIBS=" "}, and for more details if needed you can refer to the \texttt{utils/infos/Cray\_compiler\_information} directory.
You can also have a look at the configure script called:\newline
\texttt{utils/infos/Cray\_compiler\_information/configure\_SPECFEM\_for\_Piz\_Daint.bash}.

### 2023-11-15 doc/USER_MANUAL/04_creating_databases.tex
updates doc

\noindent {\bf $\bullet$ Simulation setup}
\begin{description}
\item [{\texttt{SIMULATION\_TYPE}}] is set to 1 for forward simulations,
2 for adjoint simulations (see Section \ref{sec:Adjoint-simulation-finite})
and 3 for kernel simulations (see Section \ref{sec:Finite-Frequency-Kernels}).
\item [{\texttt{SAVE\_FORWARD}}] is only set to \texttt{.true.} for a forward
simulation with the last frame of the simulation saved, as part of
the finite-frequency kernel calculations (see Section \ref{sec:Finite-Frequency-Kernels}).
For a regular forward simulation, leave \texttt{SIMULATION\_TYPE}
and \texttt{SAVE\_FORWARD} at their default values.
\item [{\texttt{UTM\_PROJECTION\_ZONE}}] UTM projection zone in
which your model resides, only valid when \texttt{SUPPRESS\_UTM\_PROJECTION} is \texttt{.false.}.
\item [{\texttt{SUPPRESS\_UTM\_PROJECTION}}] set to be \texttt{.false.}
when your model range is specified in the geographical coordinates,
and needs to be \texttt{.true.} when your model is specified in a
cartesian coordinates. \noun{UTM projection zone in which your simulation
region resides.}
\item [{\texttt{NPROC}}] The number of MPI processors, each one is assigned
one slice of the whole mesh.
\item [{\texttt{NSTEP}}] The number of time steps of the simulation. This
controls the length of the numerical simulation, i.e., twice the number
of time steps requires twice as much CPU time. This feature is not
used at the time of generating the distributed databases but is required
for the solver, i.e., you may change this parameter after running
\texttt{xgenerate\_databases}.
\item [{\texttt{DT}}] The length of each time step in seconds. This feature
is not used at the time of generating the distributed databases but
is required for the solver. Please see also Section~\ref{sec:Choosing-the-Time-Step}
for further details.
\item [{\texttt{LTS\_MODE}}] Turning this flag on will use a local-time stepping scheme for the Newmark time scheme.
It will re-distribute the mesh partitioning to balance out elements with similar local-time step sizes.
This feature can help improve the time-to-solution when the mesh contains elements of various sizes,
in particular when the mesh contains only a few very small elements that would limit the global time step size.

@@

\item [{\texttt{gll}}] For a user-specified isotropic model which uses
external binary files for $v_{p}$, $v_{s}$ and $\rho$. Binary files
are given in the same format as when outputted by the \texttt{xgenerate\_databases}
executable when using option \texttt{SAVE\_MESH\_FILES}. These binary
files define the model parameters on all GLL points which can be used
for iterative inversion procedures. Note that for simulation setups with attenuation,
it will also read in the external binary mesh files for $Q_{\kappa}$ and $Q_{\mu}$.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp.
To convert one to the other see \texttt{doc/note\_on\_Qkappa\_versus\_Qp.pdf}
and in folder \texttt{utils/attenuation}, the tool
\texttt{conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90}.

@@

\item [{\texttt{APPROXIMATE\_OCEAN\_LOAD}}] Set to \texttt{.true.} if the
effect of the oceans on seismic wave propagation should be incorporated
based upon the (rough) approximate treatment discussed in \citet{KoTr02b}.
This feature is inexpensive from a numerical perspective, both in
terms of memory requirements and CPU time. This approximation is accurate
at periods of roughly 20~s and longer. At shorter periods the effect
of water phases/reverberations is not taken into account, even when
the flag is on. If you want to model the effect of a fluid-solid model
at short periods, then set this flag to \texttt{.false.} and mesh
the fluid layer explicitly in your mesher, so that it is computed
accurately and without this approximation.
\item [{\texttt{TOPOGRAPHY}}] This feature is only effective if \texttt{APPROXIMATE\_OCEAN\_LOAD}
is set to \texttt{.true.}. Set to \texttt{.true.} if topography and
bathymetry should be read in based upon the topography file specified
in the main constants file \texttt{setup/constants.h} to evaluate elevations. If not set, elevations
will be read from the numerical mesh.
\item [{\texttt{ATTENUATION}}] Set to \texttt{.true.} if attenuation should
be incorporated. Turning this feature on increases the memory requirements
significantly (roughly by a factor of~1.5), and is numerically fairly
expensive. See \citet{KoTr99,KoTr02a} for a discussion on the implementation
of attenuation based upon standard linear solids. Please note that
the Vp- and Vs-velocities of your model are given for a reference
frequency. To change this reference frequency, you change the value
of \texttt{ATTENUATION\_f0\_REFERENCE} defined (in Hz) in input file \texttt{DATA/Par\_file}.
The code uses a constant $Q$ quality factor, write(IMAIN,*) "but approximated based on a series of Zener standard linear solids (SLS).
The approximation is thus performed in a given frequency band determined based on that \texttt{ATTENUATION\_f0\_REFERENCE} reference frequency.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp.
To convert one to the other see \texttt{doc/note\_on\_Qkappa\_versus\_Qp.pdf}
and in folder \texttt{utils/attenuation}, the tool
\texttt{conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90}.

@@

If you use PML and an external mesh (created using an external meshing tool
such as CUBIT/TRELIS or similar), try to have elements inside the PML as regular as possible,
i.e. ideally non-deformed cubes obtained by `extrusion' of regular surface mesh elements meshing the
outer edges of the computational domain without PML; by doing so, the PMLs obtained will be far more stable
in time (PML being weakly unstable from a mathematical point of view, very deformed mesh elements
inside the PMLs can trigger instabilities much more quickly). \red{We have two utilities in directory utils/CPML that do that automatically
and that are very fast}. To stabilize PMLs it also helps to add a transition layer of geometrically-regular non-PML elements, in which attenuation is also
turned off (i.e. $Q_\kappa = Q_\mu = 9999$ in that layer), as in the red layer of Figure~\ref{fig:mesh_extrusion}.
Our tools in directory utils/CPML implement that transition layer automatically.\newline

>>>>

\noindent {\bf $\bullet$ Simulation setup}
\begin{description}
\item [{\texttt{SIMULATION\_TYPE}}] is set to 1 for forward simulations,
2 for adjoint simulations (see Section \ref{sec:Adjoint-simulation-finite})
and 3 for kernel simulations (see Section \ref{sec:Finite-Frequency-Kernels}).
\item [{\texttt{SAVE\_FORWARD}}] is only set to \texttt{.true.} for a forward
simulation with the last frame of the simulation saved, as part of
the finite-frequency kernel calculations (see Section \ref{sec:Finite-Frequency-Kernels}).
For a regular forward simulation, leave \texttt{SIMULATION\_TYPE}
and \texttt{SAVE\_FORWARD} at their default values.
\item [{\texttt{UTM\_PROJECTION\_ZONE}}] UTM projection zone in
which your model resides, only valid when \texttt{SUPPRESS\_UTM\_PROJECTION} is \texttt{.false.}.
\item [{\texttt{SUPPRESS\_UTM\_PROJECTION}}] set to be \texttt{.false.}
when your model range is specified in the geographical coordinates,
and needs to be \texttt{.true.} when your model is specified in a
cartesian coordinates. \noun{UTM projection zone in which your simulation
region resides.}
\item [{\texttt{NPROC}}] The number of MPI processors, each one is assigned
one slice of the whole mesh.
\item [{\texttt{NSTEP}}] The number of time steps of the simulation. This
controls the length of the numerical simulation, i.e., twice the number
of time steps requires twice as much CPU time. This feature is not
used at the time of generating the distributed databases but is required
for the solver, i.e., you may change this parameter after running
\texttt{xgenerate\_databases}.
\item [{\texttt{DT}}] The length of each time step in seconds. This feature
is not used at the time of generating the distributed databases but
is required for the solver. Please see also Section~\ref{sec:Choosing-the-Time-Step}
for further details.
\item [{\texttt{LTS\_MODE}}] Turning this flag on will use a local-time stepping scheme for the Newmark time scheme \citep{Rietmann2015,Rietmann2016}.
It will re-distribute the mesh partitioning to balance out elements with similar local-time step sizes.
This feature can help improve the time-to-solution when the mesh contains elements of various sizes,
in particular when the mesh contains only a few very small elements that would limit the global time step size.

@@

\item [{\texttt{gll}}] For a user-specified isotropic model which uses
external binary files for $v_{p}$, $v_{s}$ and $\rho$. Binary files
are given in the same format as when outputted by the \texttt{xgenerate\_databases}
executable when using option \texttt{SAVE\_MESH\_FILES}. These binary
files define the model parameters on all GLL points which can be used
for iterative inversion procedures. Note that for simulation setups with attenuation,
it will also read in the external binary mesh files for $Q_{\kappa}$ and $Q_{\mu}$.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp.
To convert one to the other see \texttt{doc/note\_on\_Qkappa\_versus\_Qp.pdf}
and in folder \texttt{utils/small\_utilities/attenuation}, the tool
\texttt{conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90}.

@@

\item [{\texttt{APPROXIMATE\_OCEAN\_LOAD}}] Set to \texttt{.true.} if the
effect of the oceans on seismic wave propagation should be incorporated
based upon the (rough) approximate treatment discussed in \citet{KoTr02b}.
This feature is inexpensive from a numerical perspective, both in
terms of memory requirements and CPU time. This approximation is accurate
at periods of roughly 20~s and longer. At shorter periods the effect
of water phases/reverberations is not taken into account, even when
the flag is on. If you want to model the effect of a fluid-solid model
at short periods, then set this flag to \texttt{.false.} and mesh
the fluid layer explicitly in your mesher, so that it is computed
accurately and without this approximation.
\item [{\texttt{TOPOGRAPHY}}] This feature is only effective if \texttt{APPROXIMATE\_OCEAN\_LOAD}
is set to \texttt{.true.}. Set to \texttt{.true.} if topography and
bathymetry should be read in based upon the topography file specified
in the main constants file \texttt{setup/constants.h} to evaluate elevations. If not set, elevations
will be read from the numerical mesh.
\item [{\texttt{ATTENUATION}}] Set to \texttt{.true.} if attenuation should
be incorporated. Turning this feature on increases the memory requirements
significantly (roughly by a factor of~1.5), and is numerically fairly
expensive. See \citet{KoTr99,KoTr02a} for a discussion on the implementation
of attenuation based upon standard linear solids. Please note that
the Vp- and Vs-velocities of your model are given for a reference
frequency. To change this reference frequency, you change the value
of \texttt{ATTENUATION\_f0\_REFERENCE} defined (in Hz) in input file \texttt{DATA/Par\_file}.
The code uses a constant $Q$ quality factor, write(IMAIN,*) "but approximated based on a series of Zener standard linear solids (SLS).
The approximation is thus performed in a given frequency band determined based on that \texttt{ATTENUATION\_f0\_REFERENCE} reference frequency.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp.
To convert one to the other see \texttt{doc/note\_on\_Qkappa\_versus\_Qp.pdf}
and in folder \texttt{utils/small\_utilities/attenuation}, the tool
\texttt{conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90}.

@@

If you use PML and an external mesh (created using an external meshing tool
such as CUBIT/TRELIS or similar), try to have elements inside the PML as regular as possible,
i.e. ideally non-deformed cubes obtained by `extrusion' of regular surface mesh elements meshing the
outer edges of the computational domain without PML; by doing so, the PMLs obtained will be far more stable
in time (PML being weakly unstable from a mathematical point of view, very deformed mesh elements
inside the PMLs can trigger instabilities much more quickly). \red{We have two utilities in directory \texttt{utils/CPML} that do that automatically
and that are very fast}. To stabilize PMLs it also helps to add a transition layer of geometrically-regular non-PML elements, in which attenuation is also
turned off (i.e. $Q_\kappa = Q_\mu = 9999$ in that layer), as in the red layer of Figure~\ref{fig:mesh_extrusion}.
Our tools in directory \texttt{utils/CPML} implement that transition layer automatically.\newline

### 2023-11-15 doc/USER_MANUAL/06_fault_sources.tex
updates doc

\begin{lyxlist}{00.00.0000}
\item [{$\mathtt{EXAMPLES/tpv16/description/TPV16\_17\_Description\_v03.pdf}$}]~
\end{lyxlist}

@@

The purpose of the Kelvin-Voigt viscosity in the dynamic fault solver
is to damp spurious oscillations generated by the fault slip at frequencies
that are too high to be resolved by the mesh. The viscosity $\mathtt{eta}$
(in seconds) depends on the size of the elements on the fault. Here
is how to set it:
\begin{enumerate}
\item Determine the average linear size of the elements on the fault plane,
$\mathtt{h\_fault}$. Usually this value is prescribed by the user
during mesh generation. Otherwise it can be found by inspection of
the mesh inside the CUBIT GUI.
\item Use the Matlab function $\mathtt{utils/critical\_timestep.m}$ to
compute\newline
 $\mathtt{dtc\_fault}=\mathtt{critical\_timestep\left(c_{p},h\_fault,ngll\right)}$.
\newline
This is the critical time step in an elastic medium for a hypothetical
element of cubic shape with size equal to $\mathtt{h\_fault}$.
\item Set $\mathtt{eta}$ in $\mathtt{DATA/Par\_file\_faults}$ to (0.1 to 0.3)$\ensuremath{\times}\mathtt{dtc\_fault}$.
A larger $\mathtt{eta}$ damps high-frequencies more aggressively
but it might also affect lower frequencies and rupture speed.
\end{enumerate}
Viscosity reduces numerical stability: the critical timestep in a
simulation with Kelvin-Voigt damping needs to be smaller than that
in a purely elastic simulation. Here is how to set the time step accordingly:
\begin{enumerate}
\item Run a test simulation without viscosity ($\mathtt{eta}$=0 and only
a few time steps)
\item Look for the \textquotedbl{}maximum suggested time step\textquotedbl{}
in \texttt{OUTPUT\_FILES/output\_mesher.txt}. This is the critical
timestep of a purely elastic simulation, $\mathtt{dtc\_bulk}$.
\item Reset the timestep of the simulation with a Kelvin-Voigt material
to a value smaller than\newline
 $\mathtt{dtc\_kv}=\mathtt{eta}\left(\sqrt{1+\mathtt{dtc\_bulk^{2}}/\mathtt{eta^{2}}}-1\right)$
\end{enumerate}
Note that in general $\mathtt{dtc\_bulk}$ is smaller than $\mathtt{dtc\_fault}$,
because elements off the fault might be smaller or more distorted
than element faces on the fault.

@@

\item Fault quantities (slip, slip rate, stresses, etc) at regular times
are stored in binary data files called $\mathtt{Snapshot\#it\#.bin}$,
where \#it\# is the timestep number. These can be read in Matlab with
the function $\mathtt{utils/FSEM3D\_snapshot.m}$
\end{enumerate}

>>>>

\begin{lyxlist}{00.00.0000}
\item [{$\mathtt{EXAMPLES/applications/fault\_examples/tpv16/description/TPV16\_17\_Description\_v03.pdf}$}]~
\end{lyxlist}

@@

The purpose of the Kelvin-Voigt viscosity in the dynamic fault solver
is to damp spurious oscillations generated by the fault slip at frequencies
that are too high to be resolved by the mesh. The viscosity $\mathtt{eta}$
(in seconds) depends on the size of the elements on the fault. Here
is how to set it:
\begin{enumerate}
\item Determine the average linear size of the elements on the fault plane,
$\mathtt{h\_fault}$. Usually this value is prescribed by the user
during mesh generation. Otherwise it can be found by inspection of
the mesh inside the CUBIT GUI.
\item Use the Matlab function $\mathtt{utils/small\_utilities/critical\_timestep.m}$ to
compute\newline
 $\mathtt{dtc\_fault}=\mathtt{critical\_timestep\left(c_{p},h\_fault,ngll\right)}$.
\newline
This is the critical time step in an elastic medium for a hypothetical
element of cubic shape with size equal to $\mathtt{h\_fault}$.
\item Set $\mathtt{eta}$ in $\mathtt{DATA/Par\_file\_faults}$ to (0.1 to 0.3)$\ensuremath{\times}\mathtt{dtc\_fault}$.
A larger $\mathtt{eta}$ damps high-frequencies more aggressively
but it might also affect lower frequencies and rupture speed.
\end{enumerate}
Viscosity reduces numerical stability: the critical timestep in a
simulation with Kelvin-Voigt damping needs to be smaller than that
in a purely elastic simulation. Here is how to set the time step accordingly:
\begin{enumerate}
\item Run a test simulation without viscosity ($\mathtt{eta}$=0 and only
a few time steps)
\item Look for the \textquotedbl{}maximum suggested time step\textquotedbl{}
in \texttt{OUTPUT\_FILES/output\_mesher.txt}. This is the critical
timestep of a purely elastic simulation, $\mathtt{dtc\_bulk}$.
\item Reset the timestep of the simulation with a Kelvin-Voigt material
to a value smaller than\newline
 $\mathtt{dtc\_kv}=\mathtt{eta}\left(\sqrt{1+\mathtt{dtc\_bulk^{2}}/\mathtt{eta^{2}}}-1\right)$
\end{enumerate}
Note that in general $\mathtt{dtc\_bulk}$ is smaller than $\mathtt{dtc\_fault}$,
because elements off the fault might be smaller or more distorted
than element faces on the fault.

@@

\item Fault quantities (slip, slip rate, stresses, etc) at regular times
are stored in binary data files called $\mathtt{Snapshot\#it\#.bin}$,
where \#it\# is the timestep number. These can be read in Matlab with
the function $\mathtt{utils/dynamic\_rupture/FSEM3D\_snapshot.m}$
\end{enumerate}

### 2023-11-15 doc/USER_MANUAL/09_noise_simulations.tex
updates doc (newlines for better conversion with pandoc)
updates doc

\item Before we can run noise simulations, we have to specify the noise
statistics, e.g., the ensemble-averaged noise spectrum. Matlab scripts
are provided to help you to generate the necessary file:
\begin{verbatim}
EXAMPLES/noise_tomography/NOISE_TOMOGRAPHY.m  (main program)
EXAMPLES/noise_tomography/PetersonNoiseModel.m
\end{verbatim}

@@

\item Create a file called \texttt{./NOISE\_TOMOGRAPHY/irec\_main\_noise}.
Note that this file is located in directory \texttt{./NOISE\_TOMOGRAPHY/}
as well. In general, all noise simulation related parameter files
go into that directory. \texttt{irec\_main\_noise} contains only
one integer, which is the ID of the `main' receiver. For example,
if this file contains 5, it means that the fifth receiver listed in
\texttt{DATA/STATIONS} becomes the `main'. That's why we mentioned
previously that the order of receivers in \texttt{DATA/STATIONS} is
important.

@@

In order to illustrate noise simulations in an easy way, one example
is provided in \texttt{EXAMPLES/noise\_tomography/}. See \texttt{EXAMPLES/noise\_tomography/README}
for explanations. \newline

@@

If your workstation is suitable, you can run the example in \texttt{EXAMPLES/noise\_tomography/}
using:\newline

>>>>

\item Before we can run noise simulations, we have to specify the noise
statistics, e.g., the ensemble-averaged noise spectrum. Matlab scripts
are provided to help you to generate the necessary file:
\begin{verbatim}
EXAMPLES/applications/noise_tomography/NOISE_TOMOGRAPHY.m  (main program)
EXAMPLES/applications/noise_tomography/PetersonNoiseModel.m
\end{verbatim}

@@

\item Create a file called \texttt{./NOISE\_TOMOGRAPHY/irec\_main\_noise}.
Note that this file is located in directory \texttt{./NOISE\_TOMOGRAPHY/}
as well. In general, all noise simulation related parameter files
go into that directory. \texttt{irec\_main\_noise} contains only
one integer, which is the ID of the `main' receiver. For example,
if this file contains 5, it means that the fifth receiver listed in
\texttt{DATA/STATIONS} becomes the `main'. That's why we mentioned
previously that the order of receivers in \texttt{DATA/STATIONS} is
important.\newline

@@

In order to illustrate noise simulations in an easy way, one example
is provided in \texttt{EXAMPLES/applications/noise\_tomography/}. See \texttt{EXAMPLES/applications/noise\_tomography/README}
for explanations. \newline

@@

If your workstation is suitable, you can run the example in \texttt{EXAMPLES/applications/noise\_tomography/}
using:\newline

### 2023-11-15 doc/USER_MANUAL/14_post_processing.tex
updates doc

For such comparisons, the following steps are recommended:
\begin{enumerate}
\item Make sure that both synthetic and observed seismograms have the correct
station/event and timing information.
\item Convolve synthetic seismograms with a source-time function with the
half duration specified in the \texttt{CMTSOLUTION} file, provided,
as recommended, you used a zero half duration in the SEM simulations.
\item Resample both observed and synthetic seismograms to a common sampling
rate.
\item Cut the records using the same window.
\item Remove the trend and mean from the records and taper them.
\item Remove the instrument response from the observed seismograms (recommended)
or convolve the synthetic seismograms with the instrument response.
\item Make sure that you apply the same filters to both observed and synthetic
seismograms. Preferably, avoid filtering your records more than once.
\item Now, you are ready to compare your synthetic and observed seismograms.
\end{enumerate}
\noindent We generally use the following scripts provided in the \texttt{utils/seis\_process/}
directory:

@@

In order to convert between SAC format and ASCII files, useful scripts
are provided in the subdirectories ~\newline
 \texttt{utils/sac2000\_alpha\_convert/} and \texttt{utils/seis\_process/asc2sac/}.

@@

After all the simulations are done, the seismograms are collected,
and the useful database files are copied to the frontend, you may
need to clean the local scratch disk for the next simulation. This
is especially important in the case of kernel simulation, where very
large files are generated for the absorbing boundaries to help with
the reconstruction of the regular forward wavefield. A sample script
is provided in \texttt{utils/}:
\begin{verbatim}
cleanbase.pl machines
\end{verbatim}
where \texttt{machines} is a file containing the node names.

>>>>

For such comparisons, the following steps are recommended:
\begin{enumerate}
\item Make sure that both synthetic and observed seismograms have the correct
station/event and timing information.
\item Convolve synthetic seismograms with a source-time function with the
half duration specified in the \texttt{CMTSOLUTION} file, provided,
as recommended, you used a zero half duration in the SEM simulations.
\item Resample both observed and synthetic seismograms to a common sampling
rate.
\item Cut the records using the same window.
\item Remove the trend and mean from the records and taper them.
\item Remove the instrument response from the observed seismograms (recommended)
or convolve the synthetic seismograms with the instrument response.
\item Make sure that you apply the same filters to both observed and synthetic
seismograms. Preferably, avoid filtering your records more than once.
\item Now, you are ready to compare your synthetic and observed seismograms.
\end{enumerate}
\noindent We generally use the following scripts provided in the \texttt{utils/scripts/seis\_process/}
directory:

@@

In order to convert between SAC format and ASCII files, useful scripts
are provided in the subdirectories ~\newline
 \texttt{utils/scripts/sac2000\_alpha\_convert/} and \texttt{utils/scripts/seis\_process/asc2sac/}.

@@

After all the simulations are done, the seismograms are collected,
and the useful database files are copied to the frontend, you may
need to clean the local scratch disk for the next simulation. This
is especially important in the case of kernel simulation, where very
large files are generated for the absorbing boundaries to help with
the reconstruction of the regular forward wavefield. A sample script
is provided in \texttt{utils/scripts/Cluster}:
\begin{verbatim}
cleanbase.pl machines
\end{verbatim}
where \texttt{machines} is a file containing the node names.

### 2023-11-15 doc/USER_MANUAL/15_informations_for_developers.tex
updates doc

\chapter{Information for developers of the code, and for people who want to learn how the technique works}\label{cha:developers}

You can get a very simple 1D version of a demo code (there is one in Fortran and one in Python):
\begin{verbatim}
git clone --recursive https://github.com/SPECFEM/specfem1d.git
\end{verbatim}

>>>>

\chapter{Information for developers of the code}\label{cha:developers}

You can get a very simple 1D version of a demo code (there is one in Fortran and one in Python):
\begin{verbatim}
git clone --recursive https://github.com/SPECFEM/specfem1d.git
\end{verbatim}
This is helpful for everyone who wants to learn how the spectral-element method technique works.\newline
